\mytitle

### 2021-12-09 paper.tex
extend text

We define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$ as
the real part of its complex continuation.  The real dilogarithm can
be mapped onto the interval $[0,1/2]$ by using the following
identities:
%
\begin{widetext}%
\begin{align}%
  \Li(x) &= \Li\left(\frac{1}{1-x}\right) - \frac{\pi^2}{6} + \ln(1-x)\left[\frac{1}{2}\ln(1-x) - \ln(-x)\right], && (x<-1), \\
  \Li(x) &= -\Li\left(\frac{x}{x-1}\right) - \frac{1}{2}\ln^2(1-x), && (-1<x<0), \\
  \Li(x) &= -\Li(1-x) + \frac{\pi^2}{6} - \ln(x) \ln(1-x), && (\frac{1}{2}\leq x<1), \\
  \Li(x) &= \Li\left(1-\frac{1}{x}\right) + \frac{\pi^2}{6} - \ln(x)\left[\ln\left(1-\frac{1}{x}\right) + \frac{1}{2}\ln(x)\right], && (1<x<2), \\
  \Li(x) &= -\Li\left(\frac{1}{x}\right) + \frac{\pi^2}{3} - \frac{1}{2} \ln^2(x), && (x\geq 2),%
\end{align}%
\end{widetext}%
%
as well as the special values $\Li(0)=0$, $\Li(1)=\pi^2/6$ and
$\Li(-1)=-\pi^2/12$.

>>>>

We define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$ as
the real part of its complex continuation.  The real dilogarithm can
be mapped onto the interval $[0,1/2]$ by using the following
identities:
%
\begin{widetext}%
\begin{align}%
  \Li(x) &= \Li\left(\frac{1}{1-x}\right) - \frac{\pi^2}{6} + \ln(1-x)\left[\frac{1}{2}\ln(1-x) - \ln(-x)\right], && (x<-1), \\
  \Li(x) &= -\Li\left(\frac{x}{x-1}\right) - \frac{1}{2}\ln^2(1-x), && (-1<x<0), \\
  \Li(x) &= -\Li(1-x) + \frac{\pi^2}{6} - \ln(x) \ln(1-x), && (\frac{1}{2}\leq x<1), \\
  \Li(x) &= \Li\left(1-\frac{1}{x}\right) + \frac{\pi^2}{6} - \ln(x)\left[\ln\left(1-\frac{1}{x}\right) + \frac{1}{2}\ln(x)\right], && (1<x<2), \\
  \Li(x) &= -\Li\left(\frac{1}{x}\right) + \frac{\pi^2}{3} - \frac{1}{2} \ln^2(x), && (x\geq 2),%
\end{align}%
\end{widetext}%
%
as well as the special values $\Li(0)=0$, $\Li(1)=\pi^2/6$ and
$\Li(-1)=-\pi^2/12$.  Within the interval $[0,1/2]$ the real
dilogarithm has the series expansion \eqref{eq:series}, which can be
written as
%
\begin{align}
  \Li(x) = x \sum_{k=0} \frac{x^{k}}{(k+1)^2}.
  \label{eq:series2}
\end{align}
%
We approximate the sum on the r.h.s.\ of Eq.~\eqref{eq:series2} using
an economized Padé approximant on the interval $[0,1/2]$ using the
\texttt{EconomizedRationalApproximation} from Wolfram/Mathematica
\cite{mathematica},
%
\begin{align}
  \sum_{k=0} \frac{x^{k}}{(k+1)^2} =
  \frac{\sum_{i=0}^7 a_iy^i}{\sum_{j=0}^7 b_jy^j},
\end{align}
%
where $y=1/4$ is the midpoint of the interval $[0,1/2]$.  The
coefficients $a_i$ and $b_j$ ($i,j=0,\ldots,7$) are listed in
\tabref{tab:coeffs}.
